%------------------------------------------------------------------------------
\chapter*{Acknowledgements}

\label{sec:ack}
%------------------------------------------------------------------------------

I would like to thank my supervisor, Priv. Doz. Dr. Markus Cristinziani for providing me the opportunity to carry out my master thesis under his tutelage, in the ERC TopCoup group, Physikalisches Institut, University of Bonn, Germany. The encouragement and guidance provided by him has helped me immensely at different stages of my thesis and also helped maintain a steady working pace, without going astray. I would also like to thank Prof. J. Dingfelder for agreeing to be the second evaluator of my thesis. 

I would like to thank all the group members: Andrea, Carlo, O{\g}ul, Sebastian, Vadim and Arshia for a pleasant and helpful working environment in the group. My special thanks are due to Andrea for patiently guiding me in the initial few months of the thesis; I shall cherish his friendship for a long time. My thanks are also due to Sebastian, for the time and effort taken in reviewing this thesis. It is definitely a much better version now due to his numerous comments and suggestions.

I would like to mention the contributions of my close friend Saba Zia Hassan, who always managed to bring a smile in me and has been an immense source of care and helped me through numerous low moments during the time spent in Germany. She brought sunshine and fun into all those dreary moments and helped me get through the difficult times. Another special person deserving mention is Vasanth, whose friendship has meant a lot to me and has always believed in me and is my closest confidant. I shall remember fondly all the times we spent together. 

Lastly, but definitely not in the least measure, I would like to thank my parents who have supported me in my desire to study physics in Germany, despite immense amount of personal hardship, sickness and sacrifices. I owe to deep debt of gratitude for their love, care and support. 
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
